Concurrent Priority Queues

### 2014-03-29 presentation/presentation.Rnw
Sundell/Tsigas

\begin{frame}{\nameref{sec:lockfree}}
\framesubtitle{\citeauthor{sundell2003fast}}
% TODO: Short summary only?
\begin{itemize}
\item
\end{itemize}
\end{frame}

>>>>

\begin{frame}{\nameref{sec:lockfree}}
\framesubtitle{\citeauthor{sundell2003fast}}

\begin{itemize}
\item First lock-free \ac{PQ}, linearizable, \ac{SL}-based, distinct priorities
\item Deletion flag packed into least significant bits of \lstinline|next| pointers
      prevent insertion \emph{after} deleted nodes
\item Helping mechanism ensures only a single logically deleted node exists at any time
\item Performs significantly better than the \citeauthor{hunt1996efficient} heap, slightly better
      than a SkipList protected by a global lock
\item \fullcite{sundell2003fast}
\end{itemize}
\end{frame}
